\input book

\centerline{\bf Distance}
\centerline{\it Thursday, 2017/03/16}



\break


A tall woman with short black hair, bobbed into a ball, walks away
from me towards the door.  I can't imagine the man she's with
comprehends her depths.  At least I imagine depths, there, like the
image of the Mata Hari she envisages.

His problem is that he doesn't look.  He doesn't open his eyes.  The
world of blokes and buds has him surrounded by kettle fish and snare
drums.  He doesn't imagine beyond the far bank of the brook that he's
grown up beside.  He imagines that travelling past the points to which
he has grown roots would render him unrecognizable, and thereby
vulnerable and unable to defend the territory within which he keeps
his family.

My problem is that I miss mine.  Terribly.


\break

What's so great about a boy to a girl?

What's so great about a girl to a boy?

Well, in the ordinate case, they're not the same.



\break


Mathematics is the pure thought?  By it's own admission it has no
object.  Such a degree of purity discards thought, I submit.  That an
element of thought collapses to a point, as the elements of
mathematical language, a coincidence of awareness and description.
Mathematics is that degree of freedom that differentiates the
quaternion from the vector, a foundation with a structure.  The high
science is objective.  It is physics.  It was the reinvention of
physics from 1895 to 1911 that held us in a gasp of breath for a
century.  What was objective changed under it because we had not yet
wrought of it a foundation, an epistemology of existence (I submit).


\break

A woman sits nearby who has long dark hair and heavy eyeglasses that
weigh on her features with interest.  Her presence reflects the art of
the pilpul, the debate without conclusion.  The exercise of the art of
the debate and further, the art of the issue.  One could uncover
further reflections from one particular chapter of one particular
book, but I do not.  Rather it is enough to think of her as Rebecca or
Ruth, sitting alone at night with her computer.


\break

Harold looked into his lunar nadir through the optically transparent
floor in his waverider.  The Sea of Tranquility and Maskelyne crater
slid by.  He thought of her.

\break

I'm a terrible accountant.


\break

I can't handle anything like an emotion.  It's nuts.  O.K., so I keep
my distance from well known problem regions of the interwebs.  But
Cassini images with color?  Oh, wow.  That's data.




\bye
