\input book

\centerline{\bf Distance}
\centerline{\it Monday, 2017/03/13}



\break

﻿Most of which could not be recorded, however, the Antimaterialist
Manifesto was posted by mail to the offices of the press, there, where
it would be printed.  That being done, it stood to reason that the
afternoon was free.  Free of the little things that can clutter the
day light hours and obscure the sights that stand to be seen.

\break

﻿There had been a bathroom, there.  A four inch tile wall, bathtub,
molded.  I was spraying the showerhead on the grey mold, trying to
clean it.  I wanted to use this bathroom.  But there was nothing more
than a room, sheetrock, flat medium grey paint traced with outlines of
bath fixtures.  Without plumbing.

\break

﻿It's more than art.  It's a line through a spell of breath and a coin
of success.  Were it not so, the art would be but that.  A surface
hung over the manifold of intent and purpose such that we feel the
breath of ourselves and others as one in the same.

\break

﻿Exhausted story.  Freak shits floor.  Loathe to feed it peanut butter,
anything it can digest and pass.  Makes life intolerable.  When will
it learn to shit in toilet.

The rage of exhaustion.  The rage of frustration.  The waste.

\break

﻿I don't mind the force of it.  Disturbing or even disturbed.  I mind
the loss of it.  Time.  But it's time lost to life, you see.

I'm not sure I understand.  The picture is plain enough.  But this
state is too bare to envelop that state.  I'm facing a certain waste,
and an alterior benefit.

To see the benefit is not simple.  It's an art of life in art,
therefore it's necessarily subtle.

Art is subtle, it illuminates the limits of awareness.  The actor with
the freedom to bring art into life and life into art is a creature
possessed of art, in a sense.

We many find expression valued.  It is the same, on a larger canvas,
with a larger palette.

\break

﻿The only faith I've ever found has been in high places, often known by
an appearance of distance.  In contrast, the individual.  Faith, here,
valuable.

\bye
