\input book

\centerline{\bf Distance}
\centerline{\it Sunday, 2017/03/12}


\vfill
\break

﻿The strings of a violin.  A beat of a piano.  A melody of lung and
heart.

My arms crossed.  My voice silent.  

Listen.

\vfill
\break

﻿Having waited a respectable period, and having established ourselves,
what value has our further waiting?  Has your public persona taken
enough time from your actual persona?  Or will we march in this parade
of root beer floats forever?

\vfill
\break

﻿This distance has me in a strange place.  A peculiar vulnerability,
having my heart in public, dealing with other peoples' problems,
employing rouge and ruse to walk our (my) situation through the time
of changes personal and impersonal, private and public.  It's
disconcerting and on-putting and off-putting, comfort and discomfort,
familiar and unfamiliar.

So phi, $\phi$, love, $\lambda$, strange love, $\phi\lambda$.  

The disposable intellect balancing over feet as hands that grasp the
matters of art and life to integrate art and life and awareness with
force and energy and strength of character.  The awareness of
character necessary to another art of life, a pursuit of life, this
life.  A sense of my invariants, my character, my strengths and
capacities and wishes and aspirations and ambitions.

\vfill
\break

﻿Dearest Gwyneth,

If you're asking to come, the answer remains as always, yes, yes, a
thousand times, yes.

Catch me here, catch me there.  Have no fear of it!  What's the worst
that could happen?  To be caught with a chest full of squirels rather
than eyes full of tears.  Who knows which it will be.  Both?

All I know is that it needs to be like that.  A bit off customary.

All my love,

John

\vfill
\break


I just formed my first subconscious, frustrated, ``Gwyyneth!''.  It's an
upgrade from a mental vacuum.  Yeaye, me.  By time I formulate the
record, the memory of how or why is gone.  Not fair, to be sure.  Just
is.  Better than nothing.  Rather a reckoning.

\vfill
\bye
