\input book

\centerline{\bf Distance}
\centerline{\it Wednesday, 2017/03/15}



\vfill
\break

﻿In the language of the couple there is substance and separation.  The
languages extant over substance and separation have qualities of
reciprocity and primacy, indirection and immediacy.  The r\^{o}le head
exhibits reciprocity to the r\^{o}le tail with the satisfaction of
need, subject to separation.  As couple separation narrows, r\^{o}le
differentiation narrows and r\^{o}le characterizations diminish.
Reciprocity, indirection, and separation are replaced by primacy,
substance, and immediacy.

Condensing the mysteries of the communication of the couple to a
paragraph presents a grand challenge to the reader, not unlike
learning a skill.  Evolutions through the art develop understanding
until textual separation or discord spells relief from the commitment
to study.

The purpose of such a paragraph is to communicate understanding and
thereby comprehension.  Alternatively, to issue a warning to others
who pass this way.

\vfill
\break

﻿An ambition of mating or partnering or binding with another is a need
to discover another of the kind.  The concepts of spectra,
measurement, comparison, and discipline are vital.

The partner measures roughly to your magnitude in available
dimensions.  These dimensions have no name and no description.  They
are felt more than known.  The truth is a personal mystery that lies
within, beyond the resolution of terms.  An enumeration of dimensions
would fail due to the complexities with which we partner and mate.
There is no reasonable expectation of objectivity.  However, there is
a cause for comparison, relativism, and measure.

The student of these precepts must consider the measure of another as
the objective means of comparison of alternatives.  It is a cold
business.  This is the best guidance available.  From some modest
distance, the candidate for your admiration may appear to mind in the
cold light of weight or measure whereby one sees or understands some
internal metaphysical quantities.  The appearance of success and
failure are only known subliminally as they rise from the interior to
meet the consciousness of intellect.  But they are known, within, and
this knowledge is best taken seriously as the only guidance available.

\vfill
\break

﻿With the partner, the communication of the couple transcends
indirection or reciprocity of substance to immediacy or primacy of
substance.  With the partner there exists known (felt) metaphysical
bandwidth or comprehension necessary to coordination and
communication.  With the partner, thoughts of expression ``that only
make sense inside my head'' will make sense.  With the partner one
takes leave of one’s senses to join the partnership, realizing (the
bandwidth of) immediacy and primacy and substance.

\vfill
\break

﻿It takes a lot of time.  We can use the time.  We know the time.

In the time of centuries (of days) we give manifest (birth) to our new
self (existence).  It is painful.  We all know of these things,
intuitively, making it painful to watch.

Therefore we give by this documentation.  By this record our divinity
might be denoted: elements of thought collapsed to points.  Elements
of humanity shared that readers may benefit.

On this road a modus operandi.  The suspension of conclusion for the
purpose of research and development.  The production of expression
that awaits its recognition.  The language that follows recognition of
expression and abstraction of substance.  Ultimately the method of
joining, binding, mating, partnering.

The days blur over dimensions of it.  The manifestation of this real
and that real.  What is real as the identification of elements of
thought, cause and effect.  Not the binding as once discussed, but the
binding as once alluded.  Not the reading as could have been marked by
knaves and knives, but the reader as praised and honored and valued
and so, seated.

\vfill
\break

﻿My eyes look skyward in hope, through hair and cloud, over the rims of
my eyewear with the force of my heart.

This is my life, and it is your life, too.  My version is ``in the
large'', and your version is ``in the small''.  Or, as you call it,
``public life'' and ``private life''.

A distinction resting on the coin of success rather than the art of
being.  The time necessary to cross the river part art, part coin.  Of
body and mind, in a view of art not coin.  And in a coin, where art
meets mine.

And in this challenge not a knave?

Perhaps.  Of knives and tongues, to be sure.

It is art.  It expresses well.  A voice of truth and bearing.  What
would be art were it clear of infidelity.

That we carry others by our openness a certain fact.  The openness
that would be exploited by infidelity, so problematic as to consume a
year of life in the large, and entire lives in the small.

\vfill
\break

﻿In this sky a meditation and reflection, an effort of the kind.
Looking, seeming, and being recycled to the study of tools and things,
voices and rings, glyphs falling out and radioactive dust settling,
shelter and refuge and hallowed hall.

A character of being suited to a realm of thought (not of the world).

It is the cause of fidelity, that most characters of being are ill
suited to the world by intent of execution and purpose of competition,
exclusion, extortion.  Are any suited to it, each by its own
respective actuality.  Not likely.  With so many committed to a
reality of mutual exclusion, where fairness is a crime and openness a
sin.

And not of the world, a delegate from that realm (of thought) where
fairness is kind and openness a virtue.

It is the cause of fidelity, that material and spiritual be
recognized.  Knowing subjective depends on context metaphysical.
Knowing objective depends on context physical.  And in this fidelity,
breath.

Joined, in this way, an entity in fidelity.  

A partnership realized in the primacy of the art of being, where each
gives to the whole spirit without reservation, and finds within the
whole spirit without conflict.  Where each sees in the other the whole
spirit, and subscribes oneself to the whole spirit.  Where each sees
the other as itself, and subscribes oneself to itself.  Where the
strange indirection is discarded for the loving trust and commitment
of soulful partnership.  Where touch and word heal with the capacity
of self.  Where love can touch.  Where life can breathe.  Where one is
never missing and always found.

\vfill
\bye
