\input book

\centerline{\bf Distance}
\centerline{\it Tuesday, 2017/03/14}



\break

﻿The issue had been a fear of eyes, of seeing others as types by habit
or learning.  The lesson, generally people will appear or not.

That eyes open would be time consuming.  Unprepared for that am I.
Too many issues unstudied.  Fear.  Self.  Capabilities.

No choice?  Not really.

\break

﻿A Peugeot carries itself around a bend of highway, lost in a sea of
distractions, its tires inflated, its paint painted, its driver and
its cat.  He slows the car, pulling it onto a concrete median, and
stops.  The door opens and the black feline descends.  It squats
beside the curb and pees.  It finishes and the driver scoops it up,
closes the door, and rests his foot beside the gas pedal.  A stack of
papers and things of his arm beside his hand, he imagines a friend.

\break

﻿It's snowing again, today.  Not in flakes, but crunch balls.  Like
micro hale.  Little white snow balls.  They might bounce when they
impact.

Coming down twenty to fourty five degrees above the northern
horizontal.  Pretty.

There's more likely to be a diesel pickup truck around here.  The
sounds of a highway are always chilling.  Not a place for someone's
body.  This highway passes through a place not so cold.  Quite warm,
by its own accord.

\break

﻿Should I be there?

Head rests.  Eyes close.

\break

﻿The snow accumulated, sublimated, and the temperature dropped with the
sun to the horizon.  Poetic, but cold.  These thermal bags that I live
in have been cooling off as the body has been lowering its heat
output.  Not ideal.  I wrap them over head until a vent forms, invaded
by grey hair.  The western horizon darkens.

\break

﻿Moisture on the windows is starting to freeze.  It feels hard and
ripply, and is still wet.  I can't imagine that the windows won't be
glazed in icy snow crystals by dawn.  Typically the low temperature of
the day is four A.M., and around here it drops precipitously during
the night.  An aggressive evening chill followed by a typical night
could spell, guessing, twenty degrees farenheit before dawn.

\break

This affair of the heart.  So much time spent apart.  Lifting and
cleaning.  Loving and crying.    

More experimentation leading to more understanding, more understanding
leading to more comprehension.

At the limit over the convergence, continuously.

\break

Straining to see through the hair down to my nose.

\break

Time spent in church moves me forward by a step.

\break

Sailing the seas of life we take the heart down many roads and
encounter the heart at many turns.  The roads and turns are always
there, the heart is always there, but the knowing of each road and
each turn is not.  Sometimes we find a new road and a new turn and
wonder at the sight of it.  Surprised at the sight of it.  Therefore
we study it.  Is it right and well and good what my imagination shows
me that I will do?  Of course we study it.  

When the heart is well and good of it, and especially when it is of
this well of energy and power, then we know it is well and good.  This
is how we know it is well and good and why fidelity to the breath of
life is important, that we know the heart and we know the heart is
true.

\bye
