\input book

\centerline{\bf Distance}
\centerline{\it Thursday, 2017/03/23}



\vfill
\break


There is a hole in the cultural soul lost to its sense of earth and
nature and community and society.  This hole severs the connection
between instinct and awareness and consciousness and action and
reaction, expression.  The holding and letting go of others.  The
loving and respecting of others.  


\vfill
\break


The language of music combines temporal and aural discipline with the
sight of its notation.  The language of mathematics combines the
discipline of intellect and cognition, learning, with the sight of its
notation.  The language of cinema combines the discipline of being
with the technology of seeing.  

The reproducibility of understanding and comprehension and belief
known to art and science are distinct from the immediacy of learning,
and the practice of life.

The effort of creation is a state of being, consciousness, and
discipline of expression.

The practice of existence occurs within the primacy of the mind-body
identity.  Within the experience of existence, the mind-body identity,
unity, practices the arts of being and technology.

Being and technology are differentiated by reproducibility.  This is
art and science.




\vfill
\break


The practice of existence, being, has its unique independence from the
experience of existence.  

The practice of art, expression and voice, has dependence on the
experience of existence.  Art is an existential manifestation, as is
material life.

When the realization of the social individual in the material domain
is balanced with the realization of the individual mind-body identity
in the spiritual domain, being is found to be the foundation under the
instrument that experiences and expresses.  

This is the consciousness of being and sensing.

% And, the prerequisite to the practice of subjective logic as a
% discipline.


\vfill
\break


A partner within the consciousness of being, where the outer
consciousness interacts with the inner consciousness, is bound
permanently.


\vfill
\break


The temporal practice of existence, the path or journey of life, is an
existential manifestation.  The fluid consciousness evolves
continuously through thought and experience and reflection and
interaction.  Its terms are individual, and accord to the thoughts and
beliefs of the individual.


\vfill
\break


A joined existence in the primacy of being, where touch and word heal
with the capacity of self, where love can touch and life can breathe.
Where one is missing and always found.  

This self breathes, and in this way communicates.  The languages of
the couple suffer neither substance nor separation.  R\^{o}le
characterizations and differentiations have given way to the primacy
of being.  

A character of being suited to a realm of thought, and not of the
world.


\vfill
\bye
