\input book

\centerline{\bf Distance}
\centerline{\it Friday, 2017/03/24}



\vfill
\break


﻿In the experience of existence is the processes of being, sensing,
finding, and knowing.  In love, an experience of existence, we know
the partner in being through sensing and finding.  In the experience
of partnership, we don’t have an objective process of identification
and characterization.  In partnership, there is a subjective, whole
spirit, process of being and sensing and finding and knowing which is
repeated hourly and daily.


\vfill
\break


﻿They are in a state of conflict.  The denial of the existence of the
personal identity, the ignorance of the personal spirituality,
manifests in madnesses and insanities.  A sentient will not ignore the
liability.  The animus has facilities for monitoring, and adapting to
such risks, including the capacity for self awareness and intelligence
and consciousness.


\vfill
\break


﻿In being, we sit on the earth where others have sat.  We sense the
others that we might be.  In this is love and respect, admiration and
affection.  In this is distance and regard, embarrassment and
distrust.


\vfill
\break


﻿Disbelief and denial exist, today, as infidelity to the mind-body
identity, unity, the breath of life.  This infidelity manifests
through the suspicious rationality that would substitute objectivity
for subjectivity, science for art, ideology for thought, conformity
for creativity.  The rationalization of identity betrays the self, the
breath of life, the will to dispose of the gift of life according to
one’s thoughts and senses and ambitions.  

And it follows, directly, that the rationalization of economy betrays
humanity.  However, this is the ultimate conclusion of a line of
thought from the individual as a mind-body identity and a
socio-economic identity who participates in any of an infinite variety
of ways in the spiritual and material dimensions of existential
manifestation.


\vfill
\break


Throughout the millenia, the subjugation of the individual has met
with failure.  In this past millenium we turned into the problem, and
eventually arrived at the solution.  The individual can no more be
subjugated by another as by itself.  

There is an inner consciousness that demands peace and love and
respect and dignity.  It is independent of the intellect and
objectivity of the outer consciousness, which can hear its voice.
Indeed, others can hear its voice.  It is the origin of the force of
life, and it is the fountain of the energy of life.  It is the subject
of the pages of history.


\vfill
\break


The difference between the obvious and the apparent lies within the
capacity to identify, characterize, to weigh, to sense the existence
of avenues of exploration and development leading out from a vertex of
experience, knowledge, art, or science.

That history writes of the subjugation of the individual is obvious,
or at least well known.  That the lessons of history make apparent the
inutility or disservice of the exploitation of the individual should
be obvious and well known.


\vfill
\break


The alignment of the individual requires the recognition of the
primacy of the self.  The alignment of society requires the
recognition of the primacy of the individual.  When we recognize and
inhabit these basic truths, we are healthy.

An effective expression for the health of an individual system of
consciousness is the (asexual) spectrum of centers of consciousness
described by a nondeterministic equation of the spiritual state of
being, as in the following.
$$\displaylines{ \psi = \alpha + \beta + \gamma, \cr \psi = \alpha \times \beta \times \gamma.}$$

This foundation for a {\it logical epistemology of existence}, or {\it
logical existentialism}, represents the knowledge of self awareness as
the knowing of the substance and significance of (the centers of)
consciousness.

We know when we are relatively healthy by the feelings of freedom and
justice, and perhaps happiness, joy, peace and love.

These simple truths are not unlike the simple truths known to physics.
We have established the knowing of knowledge, the sense of language,
the finding of comprehension, and the holding of belief in order that
we might recognize the primacy of the individual and (of)
consciousness.



\vfill
\bye
