\input book

\centerline{\bf Distance}
\centerline{\it Monday, 2017/03/20}



\vfill
\break

Context is a logical requirement of an existential epistemology, as
found throughout natural language.  \break The preface is that
employment of the term psychology that represents the acquisition of
character from another, in person.  Undiscovered, unrevealed, the
process remains an unconscious element of being in the existential
domain.  Revealed, the process may be mined for further value of
insight.

Projection is a common subject of psychology.  It is important to the
individual to understand the context of interpersonal awareness or
communication as immediate or indirect, passive or aggressive.
Projection is the sublimated form of indirection.  In its na\"{\i}ve
forms, projection and indirection are aggressive.  

In the informal subjective modes of speech, indirection and projection
mark expression.  A reader in a normal, immediate mode of reception is
offended.  An indirection or projection is not immediate and is
therefore relatively absurd.  The conscious reader discards the
offense, coloring the emission hostile.  The unconscious reader may
react with hostility.  This reaction may be a desired exploit on
behalf of a predatory behavior.

The essays and imaginings of projection are \break counter-theory
within the study of cinematic expression.  Obviously, the film maker
requires expertise in the push and pull, turning and twisting that are
the products of cinematic expression.

An imaginary mixing of association between psychological and genetic
projection is a common subjective delusion, and component to the
aggression inherent in emotionally immature males with genetic
frustration.  In this case, the genetic entity is coupled to the male
sense of reproduction.  The sense of reproduction is primarily
concerned with the knowledge of one's genetic issue.  The feminine
knowledge of genetic issue contrasts to the masculine knowledge of
genetic issue.  The masculine genetic frustration is intelligence.
Conversely, the feminine knowledge of genetic issue is secure.

The domain of projection is this intelligence.  It is insecurity and
absurdity from the conscious perspective because it lies within a {\it
subconscious unknown}, the manifestations of an inner consciousness
demanding peace from its outer consciousness.  

Denied, the intellect will substitute a rational world view.  Ayn Rand
has this place in literature.  As counter-theory her work is too
subtle to produce a reflection of the demonstrated facilities of
projection.  The effort is not conscious.  It presents the denial of
self for the material realization of the social individual.  

Ideally, the material realization of the social individual is balanced
with the spiritual realization of the individual identity -- of the
mind-body identity, and the spiritual health of the human being.

%(isn't it ironic, discussing denial while we're initiating the practice
% of denial in this relationship.  not healthy!  instrument obscura!)%



\vfill
\bye
