\input book

\centerline{\bf Distance}
\centerline{\it Saturday, 2017/03/25}



\vfill
\break


The scene laid out, perverse.  That children were capable, chilling.  I still remember how to write such description.

\vfill
\break


It is that they, many, are not worth a look.  A moment's passing
curiosity.  It is to have learned how many are not coherent enough to
express joy, how many fake it, and then to have the need to write of
it such that the last sight of it, of normalcy, is taken from me by
it.

\vfill
\break


The perversity of intelligence.  Of not knowing, but writing in
description.  Is it description.  It needs another label, title.
Fiction.  It is fictive.  It is figmentary.  Fragmentary.  Not the
scene and its discord, but the how and the why of it.  That it comes
from one tiny little mind, tortured into the passing of gas.  Tortured
to the writing of text.  This is what they see, what they act out,
represent, in their actions.  The children whose voices fill the
night.  Who refuse to be seen.  Who, by this description, are not
there.  Another sound, another word.  Another cold chill runs down the
spine of it.

Some sound that lost sight of the fiction.


\vfill
\break


A dominatrix.  A performer of tricks.  A manipulation of power to the
conscious purpose of art.  A use of art power for the conscious
performance of fidelity, tested by the performance.  The test so
demanding on the senses as to compell the ejecta of the unhealthy, the
surprising, and the fascinating.


\vfill
\break


Where's the offence that it should not bite the \break sound if it.  It is
there, plainly writ.  So, you see, that we would not learn, an error.
That we would not see, a crime.  For how else to pass the time, but to
twist and roll, and by it to piss and shit.


\vfill
\break


Oh, this street.  This path.  This road.  This dirt track paved with
tulips and daffodils.

How do you know.  You don't. 

I come from there, and write till here.  As have texts before me.  The
sin in that is less than the glory of learning and more than the crime
of ignorance.  It is being and seeming.  No less than that.

Is it not sense.  

There is sense, but then the assumptions that roll through, plowing
down those stakes that mark the road under the pillow of a too narrow
learning and marked by a too familiar experience.

In this wisdom, not virtue.  In this virtue, not wisdom.

I should not run amuk.

There is a thing to say.  Something to be said.  A perspective.

It is one that accepts without judgement.

\vfill
\break


The sound of keys on a formica counter top. \break Dropped, in hand.
A feminine gesture, lacking a relatively masculine force.


The vessel of the assumptions of experience that enabled, as a tool
does, that distillation, is foul with a false or too facile
familiarity.

\vfill
\break


The gulf between the writer's discipline and the \break reader's
understanding requires the reader's humility. \break Lacking that, the
reader loses any available benefit.

\vfill
\break


She believes that she needs him.  And he believes that he needs her.
To survive.  Or, to breathe.  Not to survive, as in desperation.  But
to breathe, as in to live.

\vfill
\break


Worlds apart in their experience of the world.

Fundamentally, there's an assumption of health.  

There's an assumption of good will that is very \break American.

And then there's the development of an \break understanding of the
difference, of health, of world.  \break There's the separation of
oneself from interaction by learning, or by education, however it
occurs.  The separation of faith from na\"{\i}vet\'{e}.

They feel it in their bones.  That's what they're signing through work
and effort.


\vfill
\break


Perhaps spiritual exercise is not unlike successful (psychological)
therapy.  With exercise, the spirit is \break lifted and more agile.

In this, in our exercise, we have pulled and set the spiritual
bindings of our partnership.


\vfill
\break


To not encounter the obstruction of frustration one must exist within
the cause of spirit.  This is the inner consciousness.  One comes from
within the inner consciousness and ejects the obstructa known to the
outer consciousness.

This exercise marks the completion of the practice of the art of the
balancing of centers of consciousness, senses, and ambitions.


\vfill
\break


It is surprising how many will throw themselves into the appearance of
such an unknown.  Some of these may perceive the frustration of their
rationality, and that inner consciousness asserts the frustration into
plain view.  Some others of these may perceive the appearance of their
rationality, and that inner consciousness asserts the object into
plain view.  

Whatever the case may be, the erect existence is often met with such
perceptual violences spoken from within.  In consciousness, one meets
these according to choice or habit.  There is no inherent superiority
to the appearance of grace excepting the benefits of the appearance of
distance.  Engagement is preferable, when possible.  But, very often,
it is not.  It is impractical spiritually or materially, or both.


\vfill
\bye
